% Beamer Slides Content - Momentum Transformer Masterclass

% --- SLIDE 1: Momentum Archeology ---
\begin{frame}{Momentum Archeology: Finding the Signal}
    \begin{itemize}
        \item \textbf{Question:} Does momentum exist in Crypto at all timeframes?
        \item \textbf{The Tool:} Variance Ratio (VR) Test
        \item \textbf{Interpretation:} VR > 1 (Momentum), VR < 1 (Mean Reversion)
    \end{itemize}
    
    \begin{table}[]
        \centering
        \tiny
        \begin{tabular}{l|ccccc}
        \hline
        \textbf{Horizon} & \textbf{1h Data} & \textbf{4h Data} & \textbf{12h Data} & \textbf{1d Data} \\ \hline
        1 Day   & 0.974 & 1.117 & 1.022 & 0.977 \\
        5 Days  & \textbf{1.266} & \textbf{1.181} & \textbf{1.146} & 1.043 \\
        20 Days & 0.582 (MR) & 0.789 & \textbf{1.076} & 1.038 \\ \hline
        \end{tabular}
        \caption{BTC/USDT Variance Ratios across Horizons}
    \end{table}

    \begin{itemize}
        \item \textit{Insight:} 1h momentum is strong but short-lived. 12h data provides the most stable "long-horizon" signal.
    \end{itemize}
\end{frame}

% --- SLIDE 2: Failure Analysis ---
\begin{frame}{Failure Analysis: The Saturation Trap}
    \begin{columns}
        \begin{column}{0.5\textwidth}
            \textbf{The Symptom:}
            \begin{itemize}
                \item Training Loss pinned at exactly 0.1064.
                \item Predictions stuck at constant -1.000.
                \item Zero gradient flow.
            \end{itemize}
        \end{column}
        \begin{column}{0.5\textwidth}
            \textbf{The Diagnosis:}
            \begin{itemize}
                \item \textbf{High Learning Rate (0.001)} exploded weights early.
                \item \textbf{Tanh Saturation:} Large weights pushed activation to the limit.
                \item \textbf{Numerical Instability} in raw Sharpe Loss.
            \end{itemize}
        \end{column}
    \end{columns}
    \vspace{0.5cm}
    \centering
    \textit{Graphic Recommendation: Use research/strategy_performance.png to show the flat-line Equity Curve.}
\end{frame}

% --- SLIDE 3: Architectural Stability ---
\begin{frame}{Engineering for Stability: The Fixes}
    How we stabilized the Momentum Transformer:
    \begin{enumerate}
        \item \textbf{LayerNorm Integration:} Normalised features before the Tanh head to prevent saturation.
        \item \textbf{Per-Batch Sharpe:} Calculated Sharpe per-sample before averaging to maintain signal variance.
        \item \textbf{Learning Rate Pivot:} Reduced LR by 10x ($10^{-3} \to 10^{-4}$) for precise convergence.
        \item \textbf{Causal Masking:} Removed look-ahead bias to ensure realistic performance.
    \end{enumerate}
\end{frame}

% --- SLIDE 4: The Reality Check ---
\begin{frame}{The Reality Check: Robustness over 2021--2026}
    \begin{columns}
        \begin{column}{0.5\textwidth}
            \textbf{The Fantasy (Gross):}
            \begin{itemize}
                \item \textbf{Sharpe Ratio:} 3.65
                \item \textbf{Turnover:} 40.7x (Annualised)
                \item \textbf{Issue:} Unrealistic profits via noise-trading.
            \end{itemize}
        \end{column}
        \begin{column}{0.5\textwidth}
            \textbf{The Reality (Net Full Period):}
            \begin{itemize}
                \item \textbf{Sharpe Ratio:} 0.40 (In + OOS)
                \item \textbf{Estimator:} Abdi-Ranaldo dynamic spreads.
                \item \textbf{Turnover:} 42.0x (Stabilised)
            \end{itemize}
        \end{column}
    \end{columns}
    \vspace{0.4cm}
    \begin{block}{Regime Resilience}
        By integrating \textbf{dynamic spreads} into the Loss Function, we moved from a "jittery" high-frequency model to a stable trend-follower. The 0.40 Net Sharpe covers the 2025-2026 regime shift, proving the model survived where many noise-traders failed.
    \end{block}
\end{frame}

% --- SLIDE 5: Senior Engineer Lessons ---
\begin{frame}{Closing: Lessons from the Cluster}
    \begin{itemize}
        \item \textbf{Cluster Archeology:} Always investigate known working scripts (e.g., \texttt{tmem} vs \texttt{mem\_free}).
        \item \textbf{Provenance:} Timestamp your weights and logs. Never overwrite history.
        \item \textbf{Robustness:} Use \texttt{if executable(...)} checks. Production code must run on modern Spectre AND old Cluster nodes.
        \item \textbf{Truth over Hype:} A model that "cheats" (no mask) is a liability, not an asset.
    \end{itemize}
\end{frame}
